Meta-analysis of the Interoceptive Accuracy Scale

### 2025-08-10 analysis/Study1.qmd
more

```{r}
load("../data/Gaggero2021/data.rda")
df2 <- data |> 
  mutate(Gender = as.character(gender)) |> 
  mutate(across(starts_with("IAS "), as.numeric)) |>
  rename(
    Age=age, Heart = `IAS 1`, Hungry = `IAS 2`, Breathing = `IAS 3`, Thirsty = `IAS 4`,
    Urinate = `IAS 5`, Defecate = `IAS 6`, Taste = `IAS 7`, Vomit = `IAS 8`, Sneeze = `IAS 9`,
    Cough = `IAS 10`, Temp = `IAS 11`, Sex_arousal = `IAS 12`, Wind = `IAS 13`, Burp = `IAS 14`,
    Muscles = `IAS 15`, Bruise = `IAS 16`, Pain = `IAS 17`, Blood_Sugar = `IAS 18`,
    Affective_touch = `IAS 19`, Tickle = `IAS 20`, Itch = `IAS 21`,
    MAIA_AttentionRegulation = MAIA_AttentionReg, MAIA_BodyListening = MAIA_BodyListening,
    MAIA_Trusting = MAIA_BodyTrusting, MAIA_EmotionalAwareness = MAIA_EmoAwareness,
    MAIA_NotDistracting=MAIA_NotDistracting, MAIA_NotWorrying=MAIA_NotWorrying,
    MAIA_SelfRegulation=MAIA_SelfReg, MAIA_Noticing=MAIA_Noticing)
rm(data)
```

>>>>

```{r}
load("../data/Gaggero2021/data.rda")
df2 <- data |> 
  mutate(Gender = as.character(gender)) |> 
  mutate(across(starts_with("IAS "), as.numeric)) |>
  rename(
    Age=age, Heart = `IAS 1`, Hungry = `IAS 2`, Breathing = `IAS 3`, Thirsty = `IAS 4`,
    Urinate = `IAS 5`, Defecate = `IAS 6`, Taste = `IAS 7`, Vomit = `IAS 8`, Sneeze = `IAS 9`,
    Cough = `IAS 10`, Temp = `IAS 11`, Sex_arousal = `IAS 12`, Wind = `IAS 13`, Burp = `IAS 14`,
    Muscles = `IAS 15`, Bruise = `IAS 16`, Pain = `IAS 17`, Blood_Sugar = `IAS 18`,
    Affective_touch = `IAS 19`, Tickle = `IAS 20`, Itch = `IAS 21`,
    MAIA_AttentionRegulation = MAIA_AttentionReg, MAIA_BodyListening = MAIA_BodyListening,
    MAIA_Trusting = MAIA_BodyTrusting, MAIA_EmotionalAwareness = MAIA_EmoAwareness,
    MAIA_NotDistracting=MAIA_NotDistracting, MAIA_NotWorrying=MAIA_NotWorrying,
    MAIA_SelfRegulation=MAIA_SelfReg, MAIA_Noticing=MAIA_Noticing,
    BPQ_BodyAwareness = BPQ_A, BPQ_AutonomicReactivity = BPQ_R)
rm(data)
```

### 2025-08-10 analysis/study2.qmd
more

data <- rbind(data, make_rez(with = "ICQ", component="ICQ", name = "ICQ"))
```

@@

data <- rbind(
  data,
  make_rez(with = "BPQ_A", component="BPQ", name = "Body Awareness (BPQ)"),
  make_rez(with = "BPQ_R", component="BPQ", name = "Autonomic Reactivity (BPQ)"),
  make_rez(with = "BPQ_BodyAwareness", component="BPQ", name = "Body Awareness (BPQ)"),
  make_rez(with = "BPQ_AutonomicReactivity", component="BPQ", name = "Autonomic Reactivity (BPQ)")
  )
```

@@

p <- data |>
  mutate(sig = ifelse(p < .01, "p < .01", ifelse(p < .001, "p < .001", "N.S.")),
         dir = sign(r),
         var_Interoception = str_replace(var_Interoception, "CoughSneeze", "Cough/Sneeze"),
         var_Interoception = str_replace(var_Interoception, "HungryThirsty", "Hungry/Thirsty"),
         var_Interoception = str_replace(var_Interoception, "BruiseBlood", "Bruise/Blood sugar"),
         var_Interoception = str_replace(var_Interoception, "MusclesPain", "Muscles/Pain"),
         var_Interoception = str_replace(var_Interoception, "BreathingHeart", "Breathing/Heart"),
         var_Interoception = str_replace(var_Interoception, "UrinateDefecate", "Urinate/Defecate"),
         var_Interoception = str_replace(var_Interoception, "WindBurp", "Wind/Burp"),
         var_Interoception = fct_relevel(var_Interoception, "Original", "Hungry/Thirsty", "Bruise/Blood sugar", "Muscles/Pain", "Cough/Sneeze", "Wind/Burp", "Breathing/Heart", "Urinate/Defecate")) |>
         # Component = fct_relevel(
         #   Component, "Demographic", "MAIA", "Body", "Mood", "Maladaptive",
         #   "Schizotypic", "Autistic", "Personality", "Conspiracy Beliefs", "World Beliefs", "Lying Profile")) |>
  ggplot(aes(x = var_Correlate)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  # geom_point2(aes(y=r, color = dir, alpha = sig), size = 3) +
  geom_linerange(aes(color=dir, alpha=sig, ymax=r, ymin=0), linewidth = 1) +
  geom_linerange(aes(color = dir, alpha = sig, ymin = CI_low, ymax = CI_high, linewidth = log(N))) +
  # geom_linerange(aes(color=dir, alpha=sig, ymin=0, ymax=r, group=Sample), position = position_dodge2(width = 0.7), linewidth=2.5) +
  # geom_linerange(aes(ymin = CI_low, ymax = CI_high, color = dir, alpha=sig, group=Sample), position = position_dodge2(width = 0.7),
  #                linewidth = 1) +
  facet_grid(Component ~ var_Interoception, scales = "free_y", switch = "y") +
  scale_fill_gradient(low = "#2196F3", high = "#FF5722", guide = "none") +
  scale_color_gradient(low = "#2196F3", high = "#FF5722", guide = "none") +
  scale_alpha_discrete(range = c(0.2, 0.9), guide = "none") +
  scale_y_continuous(expand = c(0, 0), breaks = c(-0.3, 0, 0.3)) +
  scale_linewidth_continuous(range = c(3, 7), guide = "none") +
  coord_flip(ylim = c(-0.35, 0.35)) +
  theme_modern(axis.title.space = 5) +
  labs(y = "Strength of Association (std. Beta)") +
  theme(panel.grid.major.y = element_line(),
        axis.title.y = element_blank(),
        axis.line.x = element_blank(),
        axis.text.y = element_text(size = rel(0.5)),
        axis.text.x = element_text(size = rel(0.8)),
        plot.title = element_text(face = "bold", hjust = 0),
        strip.placement = "outside",
        strip.background.y = element_rect(fill = "#E0E0E0", color = "white"),
        strip.background.x = element_rect(fill = "#F8BBD0", color = "white"))
p
ggsave("figures/Figure3.png", p, width=21*0.5, height=29.7*0.5, dpi=300, bg="white")
```

>>>>

data <- rbind(data, pool_coef(with = "ICQ", component="ICQ", name = "ICQ", unequalrange=TRUE))
```

@@

data <- rbind(
  data,
  # pool_coef(with = "BPQ_A", component="BPQ", name = "Body Awareness (BPQ)"),
  # pool_coef(with = "BPQ_R", component="BPQ", name = "Autonomic Reactivity (BPQ)"),
  pool_coef(with = "BPQ_BodyAwareness", component="BPQ", name = "Body Awareness (BPQ)"),
  pool_coef(with = "BPQ_AutonomicReactivity", component="BPQ", name = "Autonomic Reactivity (BPQ)")
  )
```

@@

p <- data |>
  mutate(sig = ifelse(p < .01, "p < .01", ifelse(p < .001, "p < .001", "N.S.")),
         dir = sign(r),
         var_Interoception = str_replace(var_Interoception, "CoughSneeze", "Cough/Sneeze"),
         var_Interoception = str_replace(var_Interoception, "HungryThirsty", "Hungry/Thirsty"),
         var_Interoception = str_replace(var_Interoception, "BruiseBlood", "Bruise/Blood sugar"),
         var_Interoception = str_replace(var_Interoception, "MusclesPain", "Muscles/Pain"),
         var_Interoception = str_replace(var_Interoception, "BreathingHeart", "Breathing/Heart"),
         var_Interoception = str_replace(var_Interoception, "UrinateDefecate", "Urinate/Defecate"),
         var_Interoception = str_replace(var_Interoception, "WindBurp", "Wind/Burp"),
         var_Interoception = fct_relevel(var_Interoception, "Original", "Hungry/Thirsty", "Bruise/Blood sugar", "Muscles/Pain", "Cough/Sneeze", "Wind/Burp", "Breathing/Heart", "Urinate/Defecate")) |>
         # Component = fct_relevel(
         #   Component, "Demographic", "MAIA", "Body", "Mood", "Maladaptive",
         #   "Schizotypic", "Autistic", "Personality", "Conspiracy Beliefs", "World Beliefs", "Lying Profile")) |>
  ggplot(aes(y = var_Correlate)) +
  annotate(geom = "rect", xmin = -0.1, xmax = 0.1, ymin = -Inf, ymax=Inf, fill = "#FFF8E1") +
  annotate(geom = "rect", xmin = c(-0.3, 0.1), xmax = c(-0.1, 0.3), ymin = -Inf, ymax=Inf, fill = "#F1F8E9") +
  annotate(geom = "rect", xmin = c(-0.6, 0.3), xmax = c(-0.3, 0.6), ymin = -Inf, ymax=Inf, fill = "#E8F5E9") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  # geom_point2(aes(y=r, color = dir, alpha = sig), size = 3) +
  geom_linerange(aes(color=dir, alpha=sig, xmax=r, xmin=0), linewidth = 1) +
  geom_linerange(aes(color = dir, alpha = sig, xmin = CI_low, xmax = CI_high, linewidth = log(N))) +
  # geom_linerange(aes(color=dir, alpha=sig, ymin=0, ymax=r, group=Sample), position = position_dodge2(width = 0.7), linewidth=2.5) +
  # geom_linerange(aes(ymin = CI_low, ymax = CI_high, color = dir, alpha=sig, group=Sample), position = position_dodge2(width = 0.7),
  #                linewidth = 1) +
  facet_grid(Component ~ var_Interoception, scales = "free", space ="free", switch = "y") +
  scale_fill_gradient(low = "#2196F3", high = "#FF5722", guide = "none") +
  scale_color_gradient(low = "#2196F3", high = "#FF5722", guide = "none") +
  scale_alpha_discrete(range = c(0.2, 0.9), guide = "none") +
  scale_x_continuous(expand = c(0, 0), breaks = c(-0.3, 0, 0.3)) +
  scale_linewidth_continuous(range = c(3, 7), guide = "none") +
  coord_cartesian(xlim = c(-0.4, 0.4)) +
  theme_modern(axis.title.space = 5) +
  labs(x = "Strength of Association (std. Beta)") +
  theme(panel.grid.major.y = element_line(),
        axis.title.y = element_blank(),
        axis.line.x = element_blank(),
        axis.text.y = element_text(size = rel(0.5)),
        axis.text.x = element_text(size = rel(0.8)),
        plot.title = element_text(face = "bold", hjust = 0),
        strip.placement = "outside",
        strip.background.y = element_rect(fill = "#E0E0E0", color = "white"),
        strip.background.x = element_rect(fill = "#F8BBD0", color = "white"))
p
ggsave("figures/Figure3.png", p, width=21*0.5, height=29.7*0.5, dpi=300, bg="white")
```
